Development of Autograder For Competitive Programming Using Contestant PC As Worker

### 2019-06-30 src/paper.tex
fix all grammars by using grammarly

We named this system UGrade and implement this by develop five programs, i.e., UGServer, UGDesktop, UGCtl, UGJob and UGSbox. UGServer handle everything related to competition such as authentication, contest creation, problem creation, etc. We can consider UGServer as a server of all the workers in the system. UGServer stores all the problems, submissions and the grading results. We develop UGServer using Python with Django and use GraphQL for the API. We use Django because of its ease of use.

@@

To create isolated environment, we create sandbox utility program called UGSbox. By using UGSbox, one can execute a program inside an isolated environment and limit its resources. We develop UGSbox using Golang because its ease of use. UGSbox is used by autograder program to compiles and executes the program for grading process.

In this work, we named the autograder program as UGJob. UGJob asks UGServer for a job and do the grading process. UGJob uses UGSbox to compiles and executes the source code it receives from UGServer. We develop UGJob using Golang because it ease of use. The UGJob is deployed in every contestant computers. Every installation of the UGJob is equipped with the same compiler to improve the fairness of grading process.

The contestants can interact with the system using user interface programs, e.g., UGDesktop and UGCtl. UGDesktop is a graphical user interface program to interact with this system. Every contestant use UGDesktop to read the problem and submit their solutions. UGDesktop will execute UGJob periodically to grade the available job in the server. UGCtl is a text-based user interface program to interact with this system. Basically, UGDesktop and UGCtl have the same role in this system. We develop UGCtl just to automate the testing process. Fig. \ref{component} depict the relationship of the components we have developed.

@@

We compare the grading performance between UGrade and DOMJudge. We chose DOMJudge as the comparison because it was the most popular open source online judge system for ICPC competition. We deployed UGrade and DOMJudge in a computer with the same specification. Then we deployed fifteen computer to simulating the contestant actions. For DOMJudge, we deployed two more computers to work as autograder worker. For UGrade, the fifteen computers worked as the worker.

We created a dummy competition with single problem, e.g., polynomial multiplication. This problem was expected to be solved using $O(N log N)$ solution, but there are many other solution with different complexity. We use four types of solution to simulating contestant submission. The first and second type of solution have $O(N^2)$ complexity but have different implementation. The third solution has $O(N^{log_2{3}})$ complexity. The fourth solution has $O(N log N)$ complexity and considered as the correct solution.

@@

The fifteen computers were submitting each type of solution one by one two times. We logged every events that happen on the system and analyzed the result. In this work, we grade every submission multiple times for UGrade system. We tested UGrade nine times using three different grading size, e.g., one, two and five. We calculated the average time to grade a single submission in DOMJudge and UGrade. Table \ref{grading-time} shows the comparison between the average time to grade a single submission in each tests. Based on Table \ref{grading-time}, we know that the UGrade grades the submission faster than DOMJudge. We also know that the grading size of UGrade affects the grading performance a little bit. By increasing the grading size of UGrade, we will grade each submission slower because each submission need to be graded many times when the grading size is high. In other hand, increasing the grading size will increase the system security because the submission graded in many worker. The juries need to adjust the grading size so it is fast enough to grade a single submission and secure enough to prevent any attacks from contestants.

@@

Based on the development and testing we have done, there are some lessons we learned.
\begin{enumerate}
    \item There is a high grading performance improvement in UGrade compared to many online judge that are currently popular. This performance improvement is caused by the number of worker in the UGrade which follows the number of contestants in the competition.
    \item The grading performance of UGrade is not affected by the number of contestants but affected by the grading size number of UGrade. The high number of contestant causes the high number of worker too, thus doesn't affect the grading performance. However, the grading size number causes the number of submission doubles, thus affects the grading performance.
    \item The high number of grading size reduce grading performance but increase system security. The low number of grading size increase grading performance but reduce system security. The juries need to adjust the grading size to achieve the best result.
    \item The security of UGrade needs further research. However, we can use UGrade to organize some types of online judge competition where the contestant don't have root access to their computer such as ACM-ICPC competition.
    \item UGrade can keep the fairness of grading process even if the worker computers have different specification and performance. UGrade achieve this by comparing jury's solution and contestant's solution in the same computer.
    \item Pull-based load balancing of UGrade causes the UGServer load become very huge. The load balancing method of this system needs further research.
\end{enumerate}

>>>>

We named this system UGrade and implement this by developing five programs, i.e., UGServer, UGDesktop, UGCtl, UGJob, and UGSbox. UGServer handles everything related to competition such as authentication, contest creation, problem creation, etc. We can consider UGServer as a server of all the workers in the system. UGServer stores all the problems, submissions and the grading results. We develop UGServer using Python with Django and use GraphQL for the API. We use Django because of its ease of use.

@@

To create an isolated environment, we create a sandbox utility program called UGSbox. By using UGSbox, one can execute a program inside an isolated environment and limit its resources. We develop UGSbox using Golang because of its ease of use. UGSbox is used by autograder program to compiles and executes the program for the grading process.

In this work, we named the autograder program as UGJob. UGJob asks UGServer for a job and does the grading process. UGJob uses UGSbox to compiles and executes the source code it receives from UGServer. We develop UGJob using Golang because of its ease of use. The UGJob is deployed in every contestant computers. Every installation of the UGJob is equipped with the same compiler to keep the fairness of the grading process.

The contestants can interact with the system using user interface programs, e.g., UGDesktop and UGCtl. UGDesktop is a graphical user interface program to interact with this system. Every contestant uses UGDesktop to read the problem and submit their solutions. UGDesktop will execute UGJob periodically to grade the available job in the server. UGCtl is a text-based user interface program to interact with this system. Basically, UGDesktop and UGCtl have the same role in this system. We develop UGCtl just to automate the testing process. Fig. \ref{component} depicts the relationship of the components we have developed.

@@

We compare the grading performance between UGrade and DOMJudge. We chose DOMJudge as the comparison because it was the most popular open source online judge system for ICPC competition. We deployed UGrade and DOMJudge in a computer with the same specification. Then we deployed fifteen computers to simulating the contestant actions. For DOMJudge, we deployed two more computers to work as the autograder worker. For UGrade, the fifteen computers worked as workers.

We created a dummy competition with a single problem, e.g., polynomial multiplication. This problem was expected to be solved using $O(N log N)$ solution, but there are many other solutions with different complexity. We use four types of solution to simulating contestant submission. The first and second type of solution have $O(N^2)$ complexity but have a different implementation. The third solution has $O(N^{log_2{3}})$ complexity. The fourth solution has $O(N log N)$ complexity and considered as the correct solution.

@@

The fifteen computers were submitting each type of solution one by one two times. We logged every event that happens on the system and analyzed the result. In this work, we grade every submission multiple times for UGrade system. We tested UGrade nine times using three different grading size, e.g., one, two and five. We calculated the average time to grade a single submission in DOMJudge and UGrade. Table \ref{grading-time} shows the comparison between the average time to grade a single submission in each test. Based on Table \ref{grading-time}, we know that the UGrade grades the submission faster than DOMJudge. We also know that the grading size of UGrade affects the grading performance a little bit. By increasing the grading size of UGrade, we will grade each submission slower because each submission needs to be graded many times when the grading size is high. In the other hand, increasing the grading size will increase the system security because the submission graded in many workers. The juries need to adjust the grading size so it is fast enough to grade a single submission and secure enough to prevent any attacks from contestants.

@@

Based on the development and testing we have done, there are some lessons we learned.
\begin{enumerate}
    \item There is a high grading performance improvement in UGrade compared to many online judges that are currently popular. This performance improvement is caused by the number of the worker in the UGrade which follows the number of contestants in the competition.
    \item The grading performance of UGrade is not affected by the number of contestants but affected by the grading size number of UGrade. The high number of contestant causes a high number of worker too, so that doesn't affect the grading performance. However, the grading size number causes the number of submission doubles, thus affects the grading performance.
    \item The high number of grading size reduce grading performance but increase system security. The low number of grading size increase grading performance but reduce system security. The juries need to adjust the grading size to achieve the best result.
    \item The security of UGrade needs further research. However, we can use UGrade to organize some types of online judge competition where the contestant don't have root access to their computer such as ACM-ICPC competition.
    \item UGrade can keep the fairness of grading process even if the worker computers have different specification and performance. UGrade achieves this by comparing the jury's solution and contestant's solution in the same computer.
    \item Pull-based load balancing of UGrade causes the UGServer load to become very huge. The load balancing method of this system needs further research.
\end{enumerate}
